Species richness destabilizes trophic communities in freshwater ecosystems

### 2020-03-11 manuscript/bef_stability/manuscript.Rmd
First version of the discussion completed

```{r get-sem-tot-effect-rich}
rich_on_bm <- get_rich_on_bm(fit = bm_all_params,
  p_val_thl = 0.05)
rich_on_sync <- get_rich_on_bm_comp(fit = bm_all_params,
  p_val_thl = 0.05,
  bm_comp = "log_sync")
rich_on_cv_sp <- get_rich_on_bm_comp(fit = bm_all_params,
  p_val_thl = 0.05,
  bm_comp = "log_cv_sp")
```

@@

For the first time, we assessed the determinants of total biomass and temporal
biomass stability in empirical trophic communities at such high temporal and
spatial scales. We showed that species richness increased total biomass but 
decreased biomass stability. In particular, species richness decreased
synchrony and increased species CV ($\LaTeX$). Surprisingly, the avg trophic
level and connectance had no effects on either synchrony nor species CV.
Finally, we showed that high trophic group was more stable than low trophic
group but that high trophic was responsible for the negative stability-diversity
relationship.

Surprisingly, we found a negative relationship biomass stability and species
richness whereas there was a positive one between total biomass and species
richness. Those relationships followed a power law, meaning that they represent
respectively accelerating and decelerating functions. Overall, it contrasts
with studies in grasslands [@tilman_biodiversity_2006, @zhang_scale_nodate],
mesocosms [@pennekamp_biodiversity_2018] or other animals
[@olivier_independent_nodate] where positive relationships are typically found
between biomass stability and species richness. Even @franssen_annual_2011 found
that species rich communities are more stable than species poor in streams.

@grace_integrative_2016 found that biomass negatively linked to species richness
in grasslands, notably because of light competition. In freshwater ecosystems,
where resources are based on trophic relationship, TOCOMPLETE.

The total biomass of high and low trophic group trophic groups responded both
positively to species richness but not biomass stability TOREPHRASE. There is a
paradox where the high trophic group is overall more stable than the low but
species richness had a destabilizing effect on the former whereas a stabilizing
on the latter. @shanafelt_david_w._stability_nodate showed in a theoretical
study in trophic chains, the top trophic level is the more stable TOEXPLORE.
The comparison between our study and theoretical studies stays limited because
fishes in our system have a large diet and consume food item of several trophic
level while theoretical studies consider system in which one species of one
trophic level feeds only on the trophic level directly inferior
[@shanafelt_david_w._stability_nodate] ADD REF.

The total effect of river size on biomass stability was as negative as species richness,
indicating that big rivers had a high negative effect on stability.

@@

It was unexpected that the average population CV had a stronger negative effect
on biomass stability than synchrony [@bluthgen_land_2016;
@olivier_independent_nodate] *cf ref in bluthgen*. We see two hypothesis that
can raise this effect. First, the opportunity for diet differentiation can be
low in streams compare to other organisms. Bird species are for example quite
specialized in seed, flying or soil arthropods or mammals which gives
opportunities for independent dynamics. Plants also can achieve independent
dynamics either spatial segregation, niche differentiation. Because fish
species even piscivorous one are quite opportunistic in
their foraging. Secondly, in trophic network, amplitude of species biomass
involved in trophic interactions could covary positively TOTHINKABOUT.

@@

Our path analysis revealed that, although species richness has a strong effect on
connectance and the average trophic level, network structure had itself little
to no effect either on synchrony nor average population stability. This result
contradicts precedent theoretical studies on the relationship
between stability and network structure [@angelis_stability_1975, @may_will_1972], although
they considered different stability metrics (i.e. local stability of equilibrium
point). The reason might be that in our inferred network, network structure is
strongly constraints by assembly processes. Indeed, connectance decreased with
increasing species richness [@winemiller_must_1989, @thebault_stability_2010],
because a small fraction of links are realized because of food diet constraints.
In theoretical studies, connectance can be tuned from 0 (no links) to 1 (all
possible links are present) [@angelis_stability_1975]. SAMEFORTLVL
Finally, the biomass stability of freshwater ecosystems can be derived by
species richness because, through trophic structure constraints, species
richness determine largely network structure.

- Stability versus several studies:
  - [@zhang_scale_nodate]: productivity stability range from [0.4 to 1.4] for
    diversity range [10 to 30]
  - [@tilman_biodiversity_2006] on abundances:
    - stability range: 2 to 12
    - diversity range: 1 to 16

>>>>

```{r get-bm-tot-effect-rich}
rich_on_bm <- get_rich_on_bm(fit = bm_all_params,
  p_val_thl = 0.05)
```

@@

---
# Chapeau
---

For the first time, we assessed the determinants of total biomass and temporal
biomass stability in empirical trophic communities at such high temporal and
spatial scales. We showed that species richness increased total biomass but 
decreased biomass stability. In particular, species richness decreased
synchrony and increased species CV ($\LaTeX$). Surprisingly, the avg trophic
level and connectance had no effects on either synchrony nor species CV.
Finally, we showed that high trophic group was more stable than low trophic
group but that high trophic group was responsible for the negative
stability-diversity relationship.

---
# Negative relationship between stability and richness 
---

Surprisingly, we found a negative relationship biomass stability and species
richness whereas there was a positive one between total biomass and species
richness. Those relationships followed a power law, meaning that they represent
respectively accelerating and decelerating functions. Overall, it contrasts
with studies in grasslands [@tilman_biodiversity_2006, @zhang_scale_nodate],
mesocosms [@pennekamp_biodiversity_2018] or other animals
[@olivier_independent_nodate] where positive relationships are typically found
between biomass stability (computed as CV) and species richness. In streams as
well, @franssen_annual_2011 found that species richness increased biomass
stability. However other studies found a opposite relationship
[@yang_effects_2011] or a marginal one [@declerc_species_2006].

We found that species richness increased total biomass as found in salt
marshes, forests [@wu_relationship_2014,@shuaifeng_positive_2018]. But opposite
relation has been found in richness in grasslands [@grace_integrative_2016],
notably because of light competition. Precedent researches in plant communities
showed that the total biomass was primary driven by environmental drivers. In
contrast, we found that the species richness was one of the main driver of the
total biomass, together with the stream size and increasing avg temperature
(with decreasing altitude). The big effect of species richness is 
partly explained by its effect on food web assembly and so, avg trophic level
(`r round(.2/0.54 * 100)` % of richness effect on total biomass). The direct
positive effect of species richness on total biomass might be due to resource use
complementarity [@cardinale_species_2002] [add more direct REF]. It was however
unexpected that connectance had no effect on total biomass, because we could
imagine that connectance could also improve resource use, but this might be
true only under the assumption that all species have the same assimilation
efficiency.

We found that contrary to stream size, the effect of altitude of the river and
its avg temperature on total biomass was only indirect through community
structure (avg trophic level and connectance).

---
# Effect of environment on community structure
---

The total effect of river size on biomass stability was as negative as species
richness, indicating that big rivers had a high negative effect on stability (TO MOVE).
We found a mix of both expected and unexpected results on the effects on
environment on community structure. First, we expected that bigger and low
altitude streams had higher species richness because they might receive more
confluents streams and so more species through immigration.
Stream size increased both connectance and avg trophic level with the same
magnitude. An increase in mean trophic position of piscivorous species in
bigger rivers could explain this relation [@post_ecosystem_2000]. In our
network reconstruction, the fish-fish interactions are more resolved than
fish-resource interactions, which might explain positive effect of stream size
on connectance. @petchey_predicting_2010 predicted that temperature should
increase connectance but we did not find any relationship but temperature (and
low altitude) increased avg trophic level (**Bullshit**). 
CV of enrichment decreased both connectance and avg trophic level, while avg
enrichment (and CV of flow) increased both. The latter might by explained by
the fact that enrichment can benefit to top trophic level
[@hulot_functional_2000]. One explanation for the former is that enrichment
variation might destabilize top predators (REF or Bullshit again).

@@

Species richness decreased synchrony and increased \overline{CV_{sp}}. Species
richness can reduce synchrony through decrease of population size, thus raising
the role of demographic stochasticity [@loreau_species_2008] but also in the
case where species have different responses to environmental variation
[@loreau_species_2008]. While the effect of species richness on synchrony is
well understood, its effect on \overline{CV_{sp}} is more complex. Indeed, studies reported positive [@tilman_biodiversity_2006, ], neutral  [@jiang_different_2009, @olivier_independent_nodate] or negative relationships [@franssen_annual_2011, @olivier_independent_nodate]. Positive relationship between

In turn, we found that synchrony and \overline{CV_{sp}} both decreased biomass
stability, as predicted by the formulation of stability based on the CV
[@thibaut_understanding_2013].
However, it was unexpected that the average population \overline{CV_{sp}} had
a stronger negative effect on biomass stability than synchrony
[@bluthgen_land_2016; @olivier_independent_nodate]. We can advance two
hypothesis that can raise this effect. First, the opportunity for diet
differentiation can be low in streams compare to other organisms. Bird species
are for example quite specialized in seed, flying or soil arthropods or mammals
which gives opportunities for independent dynamics. Plants also can achieve
independent dynamics either spatial segregation or niche differentiation. Because
fish species even piscivorous one are quite opportunistic in their foraging.
Secondly, in trophic communities, species directly affect each other through
feeding interactions, and so could raise synchrony between species
[@raimondo_interspecific_2004] more than in systems where interactions happen
more in the form of competitive exploitation.

@@

Our path analysis revealed that, although species richness has a strong effect on
connectance and the average trophic level, network structure  itself had little
to no effect either on synchrony nor average population stability. This result
contradicts precedent theoretical studies on the relationship
between stability and network structure [@angelis_stability_1975,
@may_will_1972], although they considered different stability metrics (i.e.
local stability of equilibrium point). The reason might be that in our inferred
network, network structure is strongly constraints by assembly processes.
Indeed, connectance generally decreased with increasing species richness
[@winemiller_must_1989, @thebault_stability_2010], because a small fraction of
links are realized because of food diet constraints. In theoretical studies,
connectance can be tuned from 0 (no links) to 1 (all possible links are
present) [@angelis_stability_1975]. The link between the average trophic level
and species richness has been less studied. However, we can suppose that
because species richness increase total biomass, species richness also increase
both the biomass of prey available for piscivorous fishes and the biomass of
piscivorous species which in turn, increase the avg trophic level of the
community. In sum, the biomass stability of freshwater ecosystems can be
derived by species richness because, through trophic structure constraints,
species richness determine largely network structure.

---
# Trophic group
---

The total biomass of high and low trophic group trophic groups responded both
positively to species richness but not biomass stability. There is a
paradox where the high trophic group is overall more stable than the low but
species richness had a destabilizing effect on the former whereas a stabilizing
on the latter. @shanafelt_david_w._stability_nodate showed in a theoretical
study in trophic chains, the top trophic level is the more stable TOEXPLORE.
The comparison between our study and theoretical studies stays limited because
fishes in our system have a large diet and consume food item of several trophic
level while theoretical studies consider system in which one species of one
trophic level feeds only on the trophic level directly inferior
[@shanafelt_david_w._stability_nodate] ADD REF.
